\chapter{Closing Remarks}

\section{Summary}

DX-SAHP shows potential in replacing natural gas heaters. The parts that have been selected for the project include a flat plate collector featuring an aluminum absorber plate, a copper serpentine manifold, and a single tempered glass glazing. The system’s subcomponents, i.e., the hermetically sealed variable speed compressor, the electronic expansion valve and the condenser will be interconnected via copper tubing. Sensors have also been selected for the control of the mechanism and to enable the acquisition of data during the testing phase.

\medskip
With all the components selected, the project is on track for completion. Based on the preliminary calculations, the project is anticipated to be a success. Materials are currently being sourced for the construction of the model in the new year.

\section{Future Work}

Refer to the design binder for a complete Gantt Chart as well as a list of vendors contacted for the DX-SAHP project.

\medskip
The project was split into four phases:

\medskip
\begin{enumerate}[itemsep=3mm, parsep=-1mm, label=\roman*.]
    \item Engineering Research, Calculations, and Design.
    \item Material Acquisition.
    \item Assembly.
    \item Testing.
\end{enumerate}

\medskip
For the Fall 2021 semester, the background research, calculations, and design required to start building a working model were completed. The bill of materials is being finalized, and sponsor approval will be sought in the coming weeks. Due to COVID-19 supply chain and procurement difficulties, materials are being ordered as soon as possible to ensure project completion within the first week of April. Therefore, the timelines on the Gantt Chart are reflected to include additional contingency to ensure component delivery is met for the March 1st, 2022, assembly milestone. Finally, the testing and validation phase will take place for the remainder of the Winter 2022 semester to ensure the set design goals have been achieved.