\chapter{Project Management}

\section{Roles and Responsibilities of Team Members}

Each team member plays a vital role in the group:

\medskip
\begin{itemize}[itemsep=3mm, parsep=-1mm]
    \item Kerwin oversees the Project Management of the group which is to ensure that everything is going according to plan and to assist in contacting vendors and setting schedules up. 
    \item Nadia is responsible for the designing and sizing the collector. She is in charge of ensuring that the collector is functional.
    \item Jessica oversees component matching. Her role is important since without her, components may not work together.
    \item Charuka is the assembly lead. When the parts have arrived, he will be the one in the shop piecing it all together and leading us in that part of the project.
    \item Dhruvi will look directly into the control and data acquisition system. These include looking into all the flow meters, thermistors, and pressure transducers to list a few. It’s essential to have these components for testing purposes.
    \item Edwin will be the testing lead when the prototype has been finished. He will oversee collecting all the data that would be needed to support our project.
\end{itemize}

\section{Project Schedule and Deliverables}

\begin{table}[H]
\centering
\caption{Project Milestones}
\rowcolors{2}{gray!20}{white}
\begin{tabular}{|P{75mm}|P{75mm}|}
    \hline
    \rowcolor{orangeRed}
    Milestone & Scheduled Completion Date \\
    \hline
    First Iteration of Collector Design         & 28-Nov-21 \\
    Final Design with all Compatible Components & 1-Dec-21  \\
    Complete Bill of Materials                  & 10-Dec-21 \\
    Order all Components                        & 10-Dec-21 \\
    Prototype Completed                         & 1-Mar-22  \\
    \hline
\end{tabular}
\end{table}

\section{Budget for Prototype Development}
The budget for the entire project is \$10,000. This will include all the fees that will be listed in the bill of materials and all the service fees that will need to be paid to access and work in machine shops.

\section{Use of Project Resources and Contact Hours}
For this project, biweekly meetings with the sponsor and meetings with the faculty advisor were scheduled as needed.